%Proposal - The honors proposal in Mathematics

\documentclass[12pt]{article}

\usepackage[scale=0.77,a4paper,margin=.75in]{geometry}


\begin{document}
\title{Honors Research Proposal}
\author{Jacob Liddy}

\maketitle
\section{Purpose}
\quad
The intent of this project is to explore the properties of odd abundant numbers, specifically \textit{Odd Weird Numbers}. It is not known whether odd weird numbers exist, but in this project we intend on proving that if an odd weird number does exist, it must have certain properties.

Methodology includes the formal proof of mathematical theorems, and creating an algorithm for a computer to check millions of numbers. In doing this project I do not intend on proving that odd weird numbers do (or do not) exist, but I do intend on proving that if an odd weird number does exist, it must have certain mathematical properties. 

\section{Outcome}
\quad
In this project I expect to learn how to formally write and publish a paper in mathematics, and I expect to gain some expertise in number theory. Additionally, I will also learn more about Latex, the document preparation system. 

In the completion of this project, we will prove that if a weird, odd number exixsts, then it must have at least six prime divisors. There has not been much research on odd weird numbers in the last few decades, but there has been lots of research in odd perfect numbers(a highly related subject) over the past 150 years. Understanding weird numbers will lead to our understanding of prime numbers overall(One of the worlds greatest mysteries), and potentially could have surprising uses such as public-key cryptosystems.

\section{Style}
\quad
This project will be a mathematical publication, so its style will be in the usual style of mathematical papers: Written in Latex, and (hopefully) published to a journal of mathematics.

\end{document}
